Security Properties for Stack Safety

### 2021-06-28 submission3/main.tex
Little calle-save registers writing

>>>>

\subsection{Callee-saves Registers}

In some systems, rather than the caller saving the non-argument data from its registers
and clearing them (and therefore implicitly taking responsibility for protecting those data),
the callee is responsible for this. Nevertheless we may wish for those registers to be
protected, just as they would be in a caller-save convention.

Intuitively, a caller expects a callee-saved register to be unchanged on return -- but it
may change during the call, as long as it is restored. We similarly expect a callee-saved
register to be secret from the callee, except when it is copied to the stack! Both scenarios
reflect not stepwise but observational stack safety.

We begin by adding information to Call annotations defining which registers will be saved
and which are arguments. The stack pointer and the register containing the return address
should never be saved. We then extend the set of domains with ``saved'' and ``unsaved.''
%
\[\codemap \in \CODEMAPS ::= \WORDS \rightharpoonup \callmap(P \subseteq \REGS)\]
%
\[\stackDom \in \STKDOMS ::= \outside + \unsealed + \sealed{\depth} + \unsaved + \saved\]
